### 2015-01-12 src/introduction.Rnw
update without errors
introduction update

An impediments to wider adoption of mutation analysis is its
high computational cost.  The set of simple mutants for even a
moderate sized program can be very large, making mutation
analysis prohibitively time consuming.

@@

However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the field
has a serious lacuna in large scale research, both in the size of the
programs studied, and in the number and diversity of programs, which
reduces our confidence in all results. This is true for selective
mutation studies, sampling studies, and also for comparatively
newer studies that attempt to combine methods. This is particularly
worrisome if mutation analysis is to gain wider acceptance among
testing professionals. Further, quite a few of the influential
studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
were conducted on older programming languages such as Fortran, with
operators specific to the language, and are not directly applicable to
newer languages such as Java. Finally, with bytecode based mutation
engines like PIT~\cite{pitest} and Javalanche~\cite{javalanche}
(a \textit{do faster} approach for eliminating
the compilation step to gain execution speed), operators based on
source code modification are no longer applicable, and their
equivalents in bytecode need to be identified and compared with other
approaches. A detailed discussion of these issues can be found in
Section~\ref{sec:related}.

We have attempted to rectify this situation with a large scale study of real
world programs.  As detailed in Section~\ref{sec:methodology}, we sample
188 Java programs from Github, with size ranging from 50 LOC to 100 KLOC,
which should allow widely applicable statistical inferences to be made. We
provide the results from running both the original project's (presumably
human-generated) test suites and also automatically generated test suites
using random testing, increasing the applicability of our findings to both
testers in traditional development who are interested in applying mutation
analysis to suite evaluation and to researchers who seek to compare test
suites quickly to evaluate testing techniques.

One note about our, and other researchers, evaluation criteria is in
order.  We, like others, use the ability of a sample to correlate well
to the score over all mutants as a measure of sampling quality.  The
underlying reason for this is that, while many mutants have little
ability to distinguish between good and bad test suites, some smaller
set of mutants show subtle deficiencies in suites that are not clear
from, say, code coverage.  The full set of mutants obviously contains
these mutants, and correlating with (rather than matching) the
full mutation score is a strong indicator that many of these
discriminatory mutants have been preserved in a sample.

@@

\item Our study is the largest so far in terms of both the size of programs
involved (50 LOC to 100 KLOC), and the number of programs analyzed (188
unique open source projects) for mutant reduction strategies. This allows
for stronger and more widely applicable conclusions about effectiveness.

\item We compare a much larger number of mutant reduction strategies
than previous studies. We compare with respect to the predictive power
(correlation with the full mutation score), expected mutant reduction,
and the stability of the amount of mutant reduction expected. Our
sampling strategies include some that were suggested by other
researchers, as well as a few novel strategies not previously considered.

\item Our recommendations are useful for both testing researchers who
might be comparing automatically generated test suites, and software
testers in real world working to produce and evaluate manual test suites.

\item Most importantly, we find that random sampling strategies perform
better than operator selection strategies in consistently predicting the
final mutation score while obtaining stable computational reduction.

>>>>

An impediment to the wider adoption of mutation analysis is its
high computational cost.  The set of simple mutants for even a
moderate sized program can be very large, making mutation
analysis prohibitively time consuming.

@@

However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the field
has a serious lacuna in large scale research, both in the size of the
programs studied, and in the number and diversity of programs, which
reduces our confidence in all results. This is true for selective
mutation studies, sampling studies, and also for comparatively
newer studies that attempt to combine methods. This is particularly
worrisome if mutation analysis is to gain wider acceptance among
testing professionals. Further, quite a few of the influential
studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
were conducted on older programming languages such as Fortran, with
operators specific to the language, and are not directly applicable to
newer languages such as Java. Finally, with bytecode~\footnote{
A \textit{do faster} approach for eliminating
the compilation step to gain execution speed
} based mutation
engines like PIT~\cite{pitest} and Javalanche~\cite{javalanche}
, operators based on
source code modification are no longer applicable, and their
equivalents in bytecode need to be identified and compared with other
approaches. A detailed discussion of these issues can be found in
Section~\ref{sec:related}.

We have attempted to rectify this situation with a large scale study of real
world programs. As detailed in Section~\ref{sec:methodology}, we sample
250 Java programs from Github\footnote{Our dataset is 322 programs, but as of
this writing the larger projects have not completed finished running
full-mutation analysis.},
with size ranging from 50 LOC to 100 KLOC, excluding tests,
which should allow widely applicable statistical inferences to be made.

@@

\item Our study is the largest so far in terms of
both the size of programs involved (50 LOC to 100 KLOC excluding tests),
and the number of programs analyzed (250 unique open source projects) for
mutant reduction strategies. This allows for stronger and more widely
applicable conclusions about effectiveness.

\item We compare a much larger
number of mutant reduction strategies than previous studies. Our reduction
strategies include all the common and influential strategies for
random sampling, element scoped sampling, and operator selection, that
have been proposed in previous studeies.

\item Our evaluation crtieria is applicable to non-adequate test suites
which makes the results immediately relevant for real world programs with
non-adequate test suites.

\item Most importantly, we find that current operator reduction strategies
seldom perform better than random sampling of mutants, which suggests a need
for further research in this area.
